\HeaderA{tile.list}{Create a list of tiles in a tessellation.}{tile.list}
\keyword{spatial}{tile.list}
\begin{Description}\relax
For each point in the set being tessellated produces a list
entry describing the Dirichlet/Voronoi tile containing that
point.
\end{Description}
\begin{Usage}
\begin{verbatim} tile.list(object) \end{verbatim}
\end{Usage}
\begin{Arguments}
\begin{ldescription}
\item[\code{object}] An object of class \code{deldir} as produced
by the function \code{\LinkA{deldir}{deldir}()}.
\end{ldescription}
\end{Arguments}
\begin{Value}
A list with one entry for each of the points in the set
being tesselated.  Each entry is in turn a list with
components

\begin{ldescription}
\item[\code{pt}] The coordinates of the point whose tile is being described.
\item[\code{x}] The \code{x} coordinates of the vertices of the tile, in
anticlockwise order.
\item[\code{y}] The \code{y} coordinates of the vertices of the tile, in
anticlockwise order.
\item[\code{bp}] Vector of logicals indicating whether the tile vertex is a
``real'' vertex, or a \emph{boundary point}, i.e. a point where the
tile edge intersects the boundary of the enclosing rectangle
\end{ldescription}
\end{Value}
\begin{Section}{Acknowledgement}
The author expresses sincere thanks to Majid Yazdani who found and
pointed out a serious bug in \code{tile.list} in the previous
version (0.0-5) of the \code{deldir} package.
\end{Section}
\begin{Section}{Warning}
The set of vertices of each tile may be ``incomplete''.  Only
vertices which lie within the enclosing rectangle, and ``boundary
points'' are listed.

Note that the enclosing rectangle may be specified by the user
in the call to \code{\LinkA{deldir}{deldir}()}.

In contrast to the previous version of \code{deldir}, the
corners of the enclosing rectangle are now include as vertices
of tiles.  I.e. a tile which in fact extends beyond the rectangular
window and contains a corner of that window will have that
corner added to its list of vertices.  Thus when the corresponding
polygon is plotted, the result is the intersection of the tile
with the enclosing rectangular window.
\end{Section}
\begin{Author}\relax
Rolf Turner
\email{r.turner@auckland.ac.nz}
\url{http://www.math.unb.ca/~rolf}
\end{Author}
\begin{SeeAlso}\relax
\code{\LinkA{deldir}{deldir}()}, \code{\LinkA{plot.tile.list}{plot.tile.list}()}
\end{SeeAlso}
\begin{Examples}
\begin{ExampleCode}
        x <- runif(20)
        y <- runif(20)
        z <- deldir(x,y)
        w <- tile.list(z)

        z <- deldir(x,y,rw=c(0,1,0,1))
        w <- tile.list(z)

        z <- deldir(x,y,rw=c(0,1,0,1),dpl=list(ndx=2,ndy=2))
        w <- tile.list(z)

\end{ExampleCode}
\end{Examples}

